From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction

### 2015-09-20 paper.tex
Fixed FoV fixMes

The width of the human field of attention has been discussed in the literature.
Holmqvist~\cite{holmqvist2011eye} specifies that the visual human
range\fixme{field of view or field of attention?} is $ \pm  40\degree $ in the
horizontal and $ \pm 25\degree $ in the vertical.
In~\cite{walker1980clinical}, Spector provides a more detailed specification
for each eye splitting the vertical range into $ 60\degree $ the upper region
and $ 75\degree $ the lower one. Moreover, the horizontal range gets separated
in $ 60\degree $ inwards (towards the nose) and $ 95\degree $ outwards.
Previous work on visual perspective taking for social robotics
application~\cite{sisbot2011situation} propose to use a cone of 30$\degree$ of
aperture. In the present implementation, the first approach explained has been
chosen representing the field of view using a cone with such
dimensions\fixme{which one? 40deg? 25deg?}.

>>>>

The width of the human field of view has been discussed in the literature.
Holmqvist~\cite{holmqvist2011eye} specifies that the visual human
range is $ \pm  40\degree $ in the
horizontal and $ \pm 25\degree $ in the vertical.
In~\cite{walker1980clinical}, Spector provides a more detailed specification
for each eye splitting the vertical range into $ 60\degree $ the upper region
and $ 75\degree $ the lower one. Moreover, the horizontal range gets separated
in $ 60\degree $ inwards (towards the nose) and $ 95\degree $ outwards.
Previous work on visual perspective taking for social robotics
application~\cite{sisbot2011situation} propose to use a cone of 30$\degree$ of
aperture. In the present implementation, the first approach explained has been
chosen representing the field of view using a cone with an elliptical cross section 
and the dimensions stated by Holmqvist.
